Because support for each audio A\+PI is encapsulated in a specific \mbox{\hyperlink{class_rt_api}{Rt\+Api}} subclass, it is possible to compile and instantiate multiple A\+P\+I-\/specific subclasses on a given operating system. For example, one can compile both the Rt\+Api\+Ds and Rt\+Api\+Asio classes on Windows operating systems by providing the appropriate preprocessor definitions, include files, and libraries for each. In a run-\/time situation, one might first attempt to determine whether any A\+S\+IO device drivers exist. This can be done by specifying the api argument \mbox{\hyperlink{class_rt_audio_ac9b6f625da88249d08a8409a9db0d849a219517d1df90f94d07758481155bd469}{Rt\+Audio\+::\+W\+I\+N\+D\+O\+W\+S\+\_\+\+A\+S\+IO}} when attempting to create an instance of \mbox{\hyperlink{class_rt_audio}{Rt\+Audio}}. If no available devices are found, then an instance of \mbox{\hyperlink{class_rt_audio}{Rt\+Audio}} with the api argument \mbox{\hyperlink{class_rt_audio_ac9b6f625da88249d08a8409a9db0d849a28478830f42c2fd61e6c7ad498901931}{Rt\+Audio\+::\+W\+I\+N\+D\+O\+W\+S\+\_\+\+DS}} can be created. Alternately, if no api argument is specified, \mbox{\hyperlink{class_rt_audio}{Rt\+Audio}} will first look for an A\+S\+IO instance and then a Direct\+Sound instance (on Linux systems, the default A\+PI search order is Jack, Alsa, and finally O\+SS). In theory, it should also be possible to have separate instances of \mbox{\hyperlink{class_rt_audio}{Rt\+Audio}} open at the same time with different underlying audio A\+PI support, though this has not been tested. It is difficult to know how well different audio A\+P\+Is can simultaneously coexist on a given operating system. In particular, it is unlikely that the same device could be simultaneously controlled with two different audio A\+P\+Is.

The static function \mbox{\hyperlink{class_rt_audio_a1df0b60d45637f65dab961b658056503}{Rt\+Audio\+::get\+Compiled\+Api()}} is provided to determine the available compiled A\+PI support. The function \mbox{\hyperlink{class_rt_audio_a83687634795792b2c47e4ae1cf8a5246}{Rt\+Audio\+::get\+Current\+Api()}} indicates the A\+PI selected for a given \mbox{\hyperlink{class_rt_audio}{Rt\+Audio}} instance. 